### 2023-10-10 main.tex
fix

H_{right}^{'}=S_{1}H_{right}S_{1}^{-1}=
% \exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=
\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt

@@

 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
Therefore, by taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\begin{equation}\label{HSecond}
	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
that is related to $H'$ by
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
The boundary Hamiltonians of $H^{''}$ read
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
	\item $A_{N}=e_{aN}$ with $a\neq 1$
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
\item $A_{a}=e_{aa}$ with $a\neq 1$
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
Similarly, using again \eqref{HT-BA} we have for the right boundary 
			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
It is convenient to introduce also the transformation
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
This matrix $S$ connects $H$ with $H^{''}$ by 
H=S^{-1}H^{''}S
and, the relation between eigenvectors with vanishing eigenvalue is
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. 

@@

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $1$ to $N-1$. This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $s_{i}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

\textbf{Remark}: using binomial theorem we rewrite the \eqref{exactCorrelations} as 

@@

By exchanging the summations we rewrite it as 

>>>>

H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
Therefore, by taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}S_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ read
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		\\&=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		\\&=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			\\&=
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			\\&=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $1$ to $N-1$. This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $s_{i}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

\textbf{Remark}: using the binomial theorem we rewrite the \eqref{exactCorrelations} as 

@@

By exchanging the summations we rewrite as 
